---
title: "Today at a glance"
---

```{r}
source("R/weather.R")
payload <- fetch_weather()
current <- payload$current
daily <- daily_frame(payload)[1, ]
hourly <- hourly_frame(payload)
best <- best_outdoor_hour(hourly)
```

::: {.hero}
# Copenhagen weather

`r weather_description(current$weather)` · Updated `r format(as_local_time(current$dt), "%H:%M")`
:::

::: {.grid}
::: {.metric}
## Now
`r sprintf("%.0f°C", current$temp)`

Feels like `r sprintf("%.0f°C", current$feels_like)`
:::
::: {.metric}
## Today
`r sprintf("%.0f / %.0f°C", daily$max_temp, daily$min_temp)`

High / low
:::
::: {.metric}
## Rain chance
`r sprintf("%.0f%%", daily$pop)`

Wind `r sprintf("%.0f m/s", daily$wind_speed)`
:::
::: {.metric}
## Best outside
`r format(best$time, "%H:%M")`

Score `r round(best$score)` / 100
:::
:::

## The next 24 hours

```{r}
library(ggplot2)
ggplot(head(hourly, 24), aes(time, temp)) +
  geom_line(linewidth = 1.1, colour = "#6ee7ff") +
  geom_point(aes(colour = pop), size = 2.5) +
  scale_colour_gradient(low = "#a7f3d0", high = "#60a5fa", name = "Rain chance %") +
  labs(x = NULL, y = "Temperature °C") +
  theme_minimal(base_size = 12)
```

Sunrise `r format(daily$sunrise, "%H:%M")` · Sunset `r format(daily$sunset, "%H:%M")`
